Time invariant analysis of epidemics with \pkg{EpiCompare}

### 2021-03-30 jss/EpiCompare-paper/EpiCompare-paper.Rmd
attempts at section 3

\ben{[Brainstorming: (intro) discuss model vs model comparison tools, (a) highlight that standard comparisons can be done if models share metrics or parameters (and similarly some comparisons can be done to the real epidemics). (b) Present time-invariance tools that allow us to compare more types of models (and can also give new tools to assess models beyond the standard ones). (1) introduce prediction regions (a) geom_prediction_bands,  (2) discuss different extremeness measures.]}

Comparison and assessment of model fit or comparisons of one model to another model can be performed in a variety of ways including mean square error, AIC, plots, and more.  Perhaps the most useful tool \pkg{EpiCompare} has to offer to the expert, for comparison and assessment of models, is in its post-processing tools which create a standard output.  It is then a matter of writing a script or function made for that standard output to assess the results from multiple models in the way the user desires\footnote{\ben{[Ben says: Shannon, doesn't this below in the previous section?, I might drop this paragraph except for the introduction sentence - is it really true that the standardization is most valuable?]}}.

However, for those who like more concrete tools, \pkg{EpiCompare} offers functions to compare prediction regions to one another including `geom_prediction_band()` (which plots the region), and `create_{convex_hull,delta_ball}_structure()`(which returns the `R` output for the given structure), and `contained()` (which allows the user to determine if one set of points is contained in a prediction band).  Additionally, we offer ways to determine if model outputs are compatible with one another, that is how extreme one output is to another.  \shannon{Ben says something about distance}

>>>>

<!-- \ben{[Brainstorming: (intro) discuss model vs model comparison tools, (a) highlight that standard comparisons can be done if models share metrics or parameters (and similarly some comparisons can be done to the real epidemics). (b) Present time-invariance tools that allow us to compare more types of models (and can also give new tools to assess models beyond the standard ones). (1) introduce prediction regions (a) geom_prediction_bands,  (2) discuss different extremeness measures.]} -->

As introduced in Section \ref{sec:beyond-r0-sir} there's a lot of potential for time-invariant tools to help compare and assess epidemics and models/simulations. In \pkg{EpiCompare} we provide a set of comparison and assessment tools for models that extend beyond the standard performance metrics (e.g. means squared error, AIC) and focus on assessing the structural information the models capture. This approaches work well on models where online one "cycle" of the epidemic has occurred (no recovered individuals have been susceptible again). Epidemics are complex objects, and we provide tools to create prediction regions out of simulated epidemics. For 3-state epidemic models, we provide the `ggplot`/`ggtern` extension `geom_prediction_band()` which creates a prediction region around the top $1-\alpha$ proportion of the simulations (where the simulations treated as filaments). In \pkg{Epicompare} we also provide these prediction regions for epidemic models with with more than 3 states. With `create_convex_hull_structure` and ``create_delta_ball_structure` that will create different geometric representations of prediction regions and an assoicated `contained` method that assesses if a new epidemic (seen as a filament) is contained in the prediction region.

We also provide functions to calculate the extremeness of a true epidemic compared to simulated epidemics through the equi-distance filamental trajectory representation as mentioned in Section \ref{sec:beyond-r0-sir}. Specifically, functions like  `distance_psuedo_density_function` can calculate a psuedo-density estimate of the true epidemic relative to simulated ones. Functions `distance_depth_function` and `local_distance_depth_function` provide depth scores that suggest how geometrically central an epidemic is to simulations.

\ben{[Ben says: Replaced with paragraphs above.]} Comparison and assessment of model fit or comparisons of one model to another model can be performed in a variety of ways including mean square error, AIC, plots, and more.  Perhaps the most useful tool \pkg{EpiCompare} has to offer to the expert, for comparison and assessment of models, is in its post-processing tools which create a standard output.  It is then a matter of writing a script or function made for that standard output to assess the results from multiple models in the way the user desires\footnote{\ben{[Ben says: Shannon, doesn't this below in the previous section?, I might drop this paragraph except for the introduction sentence - is it really true that the standardization is most valuable?]}}.

\ben{[Ben says: Replaced with paragraphs above.]} However, for those who like more concrete tools, \pkg{EpiCompare} offers functions to compare prediction regions to one another including `geom_prediction_band()` (which plots the region), and `create_{convex_hull,delta_ball}_structure()`(which returns the `R` output for the given structure), and `contained()` (which allows the user to determine if one set of points is contained in a prediction band).  Additionally, we offer ways to determine if model outputs are compatible with one another, that is how extreme one output is to another.  \shannon{Ben says something about distance}
